---
#title: "Journal"
#output:
#  html_document:
#    toc: true
#    toc_float: true
#    collapsed: false
#    number_sections: false
#    toc_depth: 1
#    #code_folding: hide
title: ""
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: yes
    toc_float: yes
    collapsed: no
    number_sections: no
    toc_depth: 1
  pdf_document:
    toc: yes
    toc_depth: '1'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


# Objectives


# Overview

Flights :  On-time data for all flights that departed NYC (i.e. JFK, LGA or EWR) in 2013.

year, month, day Date of departure.
dep_time, arr_time Actual departure and arrival times (format HHMM or HMM), local tz.

sched_dep_time, sched_arr_time Scheduled departure and arrival times (format HHMM or HMM),
local tz.

dep_delay, arr_delay Departure and arrival delays, in minutes. Negative times represent early
departures/arrivals.

carrier Two letter carrier abbreviation. See airlines to get name.

flight Flight number.

tailnum Plane tail number. See planes for additional metadata.

origin, dest Origin and destination. See airports for additional metadata.



air_time Amount of time spent in the air, in minutes.

distance Distance between airports, in miles.

hour, minute Time of scheduled departure broken into hour and minutes.

time_hour Scheduled date and hour of the flight as a POSIXct date. Along with origin, can be
used to join flights data to weather data.

# Some Viz


# Findings






```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

